---
title: "hv_model"
author: "Corey Shono"
date: "November 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```


Import Libraries 
```{r message=FALSE}  
#rm(list=ls())
library(ggplot2) 
library(dplyr)
library(tidyverse) 
library(plotly) 
library(AppliedPredictiveModeling)
library(caret)
#library(e1071)
library(earth)
#library(leaps)
#library(boot)
#library(kernlab)
#library(randomForest) 
library(hash) 
```


Define Functions 
```{r} 
get_m_params <- function(m){
  if ("hdd_0" %in% rownames(summary(m)$coefficients)){
    h_coef <- summary(m)$coefficients["hdd_0",1] 
    h_p <- summary(m)$coefficients["hdd_0",4] 
  }
  else {
    h_coef <- NA
    h_p <- NA 
  }
  
  if ("cdd_0" %in% rownames(summary(m)$coefficients)){
    c_coef <- summary(m)$coefficients["cdd_0",1]
    c_p <- summary(m)$coefficients["cdd_0",4]
  }
  else {
    c_coef <- NA
    c_p <- NA 
  }
  
  intercept <- summary(m)$coefficients["(Intercept)",1] 
  
  r2 <- summary(m)$r.squared 
  rse <- summary(m)$sigma
  
  m_values <- c(h_coef, c_coef, h_p, c_p, r2, rse, intercept) 
  return(m_values) 
}

lm_diagnose <- function(lm_model, name=""){
  # Model Summary 
  #print(paste("Model:", name))
  #print(paste("Resid Standard Error:", summary(lm_model)$sigma))
  #print(paste("R-Squared:", summary(lm_model)$r.squared))
  
  # Histogram Standardized Residual 
  #hist(resid(lm_model)/sd(resid(lm_model)), main=paste(name, "Normalized Residual Histogram"), xlab="Standardized Residual", panel.first=grid(), breaks=23) 
  
  # QQ Plot Standardized Residual 
  qqnorm(resid(lm_model)/sd(resid(lm_model)), cex=0.5, main=paste(name, "Normalized QQ Plot"), ylab="Standardized Residual", panel.first=grid()) 
  qqline(resid(lm_model)/sd(resid(lm_model)), col="red") 
  
  #plot(lm_model, panel.first=grid())
}


```


Import Data 
```{r} 
#file_in <- "../data/hv_model_2019-09.csv" 
file_rmt <- "../data/hv_model_2019-09_rmt.csv" 
file_sp <- "../data/hv_model_2019-09_sp.csv" 

df_rmt <- read.csv(file_rmt) 
df_sp <- read.csv(file_sp) 
```

Scatter Plot of data 
```{r} 
ggplot(df_rmt, aes(x=cdd_0, y=hvac_kWh, color=Timestamp)) + geom_point()
ggplot(df_sp, aes(x=cdd_0, y=hvac_kWh, color=Timestamp)) + geom_point() 
```

It is clear from this that the first and last days of the dataset are skewed from incompleteness of data leading to a lower amount of energy measured for these days in the dataset. Therefore, we will omit the first and last day in the dataset from this model fitting. 

Remove 2019-09-04 and 2019-09-30 
```{r} 
# Convert Timestamp columns to date types 
df_rmt$Timestamp <- as.Date(df_rmt$Timestamp, "%Y-%m-%d") 
df_sp$Timestamp <- as.Date(df_sp$Timestamp, "%Y-%m-%d") 

df_sp <- df_sp %>% 
  filter(Timestamp > as.Date("2019-09-05")) %>% 
  filter(Timestamp < as.Date("2019-09-29"))

df_rmt <- df_rmt %>%
  filter(Timestamp > as.Date("2019-09-05")) %>%
  filter(Timestamp < as.Date("2019-09-29")) 

ggplot(df_rmt, aes(x=cdd_0, y=hvac_kWh, color=RLID)) + geom_point()
ggplot(df_sp, aes(x=cdd_0, y=hvac_kWh, color=RLID)) + geom_point() 
```

Based on the lack of thermostat data, and the appearance that the thermal envelope of the entire community appears to have a similar U-value, we can probably apply the same thermal model to every house in the community. 

Fit Thermal Model to Entire Community 
```{r} 
lm_eqn <- function(df){
    m <- lm(hvac_kWh ~ cdd_0, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}
ggplot(df_sp, aes(x=cdd_0, y=hvac_kWh)) + 
  geom_point() + 
  geom_smooth(method=lm) + 
  geom_text(x=5, y=40, label = lm_eqn(df_sp), parse=TRUE) 

```

FIt Community Multivarite Model 
```{r} 
community_model <- lm(hvac_kWh ~ cdd_0 + hdd_0, data=df_sp) 
summary(community_model)
lm_diagnose(community_model, "All Homes") 
```

Residuals are normally distributed based on the linearity of the normal qq-plot, so linear model is valid. 


Fit Data for individual homes 
```
m_summary <- data.frame(hdd_coef = double(), 
                        cdd_coef = double(), 
                        hdd_p = double(), 
                        cdd_p = double(), 
                        r_square = double(), 
                        RSE = double(), 
                        intercept = double() 
) 
models <- hash() # hash object containing all model objects 

for (rlid in unique(df$RLID)){
  # Filter dataset for current RLID 
  tmp <- df[df$RLID == rlid, ]
  
  # Fit linear model 
  m <- lm(hvac_kWh ~ cdd_0 + hdd_0, data=tmp)
  
  # Save Model Results 
  models[[rlid]] <- m 
  m_summary[rlid,] <- get_m_params(m) 
  
  # Plot QQ Plot 
  #lm_diagnose(m, rlid)
}
```




Plot Diagnostics for top R^2 models 
``` 
top_summary <- m_summary[order(-m_summary$r_square),] %>%
  head() 

# Plot Normal QQ-Plot for each model 
for (rlid in rownames(top_summary)){
  lm_diagnose(models[[rlid]], rlid) 
  plot_data <- data.frame(
    fitted_values = models[[rlid]]$fitted.values, 
    residuals = models[[rlid]]$residuals
  )
  p <- ggplot(plot_data, aes(x=fitted_values, y=residuals)) + 
    geom_point() + 
    geom_smooth(method=lm)
  print(p) 
}
```

This may not be the most reliable model for individual homes. 



